### 2023-01-25 manuscript.tex
more regex! [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/83ec084ea920c4a2ffc6631608fbfbe21aaa0737.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/83ec084ea920c4a2ffc6631608fbfbe21aaa0737/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4001720206

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/76f75247d47f0d152d3ef69cfed06a9feb6ff958/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/76f75247d47f0d152d3ef69cfed06a9feb6ff958}{stain/2022-fdo-paper@76f7524}
on January 25, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/83ec084ea920c4a2ffc6631608fbfbe21aaa0737/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/83ec084ea920c4a2ffc6631608fbfbe21aaa0737}{stain/2022-fdo-paper@83ec084}
on January 25, 2023.
